%% Main-Version Draft
\documentclass[12pt,a4]{article}
%% -------------------------------
%% |          Packages           |
%% -------------------------------
 \usepackage{amsmath}
 \usepackage{mathtools} 
 \usepackage{graphicx}
 \usepackage[merge,numbers,compress]{natbib}
 \usepackage[T1]{fontenc}
 \usepackage{booktabs}
 \usepackage{xcolor} 
 \usepackage{xspace}
 \usepackage{dcolumn}
 \usepackage{placeins}
 \usepackage[colorlinks=true,citecolor=blue!50!black,linkcolor=black]{hyperref}
%  \usepackage[pdfborder={0 0 0}]{hyperref}
 \usepackage{caption}
 \usepackage
 [subrefformat=parens,position=top,skip=-15pt,margin=15pt,justification=justified,singlelinecheck=false]
 {subcaption}
 \usepackage{multirow}
\usepackage{slashed}
\usepackage[bottom]{footmisc}
\usepackage{comment}
\usepackage{bigints}
\usepackage{hhline}
\usepackage[normalem]{ulem}

%\oddsidemargin 00pt \evensidemargin 00pt
%\topmargin 00pt \headheight 00pt \headsep 00pt
%%\footheight 12pt \footskip 30pt
%\textheight 232mm \textwidth 160mm

\setlength{\evensidemargin}{00pt}
\setlength{\oddsidemargin}{00pt}
\setlength{\topmargin}{0.00pt}
\setlength{\textwidth}{160mm}
\setlength{\textheight}{232mm}
\setlength{\headheight}{00pt}
\setlength{\headsep}{00pt}
\setlength{\voffset}{00pt}
\setlength{\hoffset}{00pt}
%\setlength{\paperheight}{29.7cm}

\renewcommand{\topfraction}{1.0}
\renewcommand{\bottomfraction}{1.0}
\renewcommand{\textfraction}{0.15}
\renewcommand{\floatpagefraction}{0.8}

\newcommand{\SD}[1]{{ {\color{orange}{ [SD: #1]}} }}
\newcommand{\MP}[1]{{ {\color{blue}{ [MP: #1]}} }}
\newcommand{\JH}[1]{{ {\color{violet}{ [JH: #1]}} }}
%\newcommand{\change}[1]{{{\color{red}{#1}}}}
\newcommand{\new}[1]{{{\color{olive}{#1}}}}

\newcommand{\processmue}{\gamma\gamma \to \tau^+ \tau^- \to e^+ \mu^- \bar{\nu}_\tau \nu_\tau \bar{\nu}_{\mu} \nu_{e}}

\newcommand{\process}{\gamma\gamma \to \tau^+ \tau^- \to \ell'^+ \ell^- \bar{\nu}_\tau \nu_\tau \bar{\nu}_{\ell} \nu_{\ell'}}

\newcommand{\M}{\mathcal{M}}

%% ---------------------------------
%% | ToDo Marker - only for draft! |
%% ---------------------------------
% Remove this section for final version!
% \setlength{\marginparwidth}{20mm}
% 
% \newcommand{\margtodo}
% {\marginpar{\textbf{\textcolor{red}{ToDo}}}{}}
% 
% \newcommand{\todo}[1]
% {{\textbf{\textcolor{red}{(\margtodo{}#1)}}}{}}

\newcommand{\eq}[1]{\begin{equation} #1 \end{equation}}
\newcommand{\eqa}[1]{\begin{eqnarray} #1 \end{eqnarray}}

\input{macros}

\begin{document}

\title{\hfill ~\\[-30mm]
\phantom{h} \hfill\mbox{\small FR-PHENO-2026-XXX}
\\[1cm]
\vspace{13mm} 
%\textbf{Subtleties in the determination of the anomalous magnetic moment and the electric dipole moment of leptons via ultraperipheral heavy-ion collisions at the LHC.}
\textbf{Imprint of the anomalous magnetic moment 
%and the electric dipole moment 
of the $\tau$-lepton in the $\tau^+\tau^-$ production via ultraperipheral heavy-ion collisions at the LHC.}
}

\date{}
\author{
Stefan Dittmaier\footnote{E-mail:
  \texttt{stefan.dittmaier@physik.uni-freiburg.de}},
José Luis Hernando Ariza\footnote{E-mail: 
  \texttt{jose.luis.hernando@physik.uni-freiburg.de}},
Mathieu Pellen\footnote{E-mail:
  \texttt{mathieu.pellen@physik.uni-freiburg.de}}
\\[9mm]
{\small\it Universit\"at Freiburg, Physikalisches Institut,} \\
{\small\it Hermann-Herder-Str.\ 3, 79104 Freiburg, Germany}\\[3mm]
}
\maketitle

\begin{abstract}
\noindent


\end{abstract}
\thispagestyle{empty}


\newpage
\setcounter{page}{1}

\tableofcontents
% \newpage

\section{Introduction}


\section{Features of the calculation}
\label{sec:features}


\subsection{Form-factor approach}
\label{sec:form_factor}

- Keep this section for a general lepton and focus on the $\tau$-lepton in the numerics to emphasize that the same analysis can be done for $e$ and $\mu$ as a check of the method(?).

\subsubsection{Form-factor decomposition of the $\bf{\gamma}\bf{\bar{\tau}}\bf{\tau}$ vertex function}
\label{sec:vertex}

- Mention the problem of the off-shell $\tau$ in the standard approach.

- Outline the way how the general form-factor decomposition is obtained.

- Give the general form-factor decomposition in the on-shell basis.

- Give the transformation properties under space-time discrete symmetries of each term (no details). 

- Give the from-factor decomposition in the standard kinetical configuration and in ``ours''.

- Remark that the decomposition is gauge dependent (Ward identities).

\subsubsection{Extracting the contribution from $a_\tau$}
\label{sec:a_tau_term}

- Write matrix element with the general vertex decomposition.

- Perform an expansion of the form factors in $\alpha$.

- Remark again the presence of gauge dependence in this decomposition.

- Remark the absence of effects due to real radiation in the form factor approach.

- Perform Taylor expansion of the form factors around $\frac{x}{s} \sim \frac{m^2}{s}$ ($x=t,u$) to extract $a_\tau$ and $d_\tau$ contributions.

\subsubsection{Coulomb term and Sommerfeld enhancement}
\label{sec:Coulomb_term}

- Explain the need of including the Coulomb term.

- Give the contribution from Coulomb term.

\subsubsection{Analytical expressions for the helicity amplitudes (?)}
\label{sec:analytics}

- Give analytical expression in the spinor-helicity formalism for $\M^{(0)}$, $\M^{a_\tau}$, $\M^{d_\tau}$.

\subsection{Technical aspects of the calculation and employed tools}
\label{sec:tools}

- Use of equivalent-photon approximation.

- Use of iNWA to include spin correlations.

- Use of mixed input-parameter scheme.


\subsubsection*{Checks on the calculation}
\label{sec:checks}

- Analytical expressions checked against FeynArts.

- Correct behaviour under $\mc{P}$, $\mc{C}$ and $\mc{CP}$ of $\M^{(0)}$, $\M^{a_\tau}$, $\M^{d_\tau}$  (?).

\subsection{Set-up of the calculation}
\label{sec:setup}

\subsubsection*{Numerical input}
\label{sec:inputs}

- Numerical inputs

\subsubsection*{Event selection}
\label{sec:selection}

- ATLAS set-up

\section{Results}
\label{sec:results}

\subsection{Comparison between the form-factor and the fixed-order calculation}

- Reference to the previous paper for details on the NLO prediction.

- Show the relevance of the non included effects in the form-factor approach, \ie
\begin{align}
  \Delta_\mr{FF}
  = \frac{\sigma^{\mr{FF}} - \sigma^{\mr{QED}_\mr{P}}}{\sigma^{\mr{QED}_\mr{P}}}
\end{align}

\subsubsection{Inclusive $\tau$-pair production}
\label{sec:aa_to_tautau}

- Comparison just for the production, \ie no $\tau$-decays.

- Show it just for unpolarized $\tau$-leptons.

- Mention that $a_\tau$ is part of QED corrections, which are gauge invariant independently and, thus, they can be compared.


\subsubsection*{Fixed photon--photon centre-of-mass energy}

- Show comparison for fixed c.m.e. ($3.8, 5(?), 10, 18 \GeV$? or all?)

- Remark importance of the Coulomb term for small c.m.e..

- Remark the importance of using observables that are not sensitive to collinear radiation off the produced $\tau$-leptons.


\subsubsection*{Ultraperipheral heavy-ion collision}

- Show comparison with photon flux.

- Mention the problem in Ref.~\cite{Jiang:2024dhf}: 

 * Wrong input-parameter scheme $\to$ Fixable by considering the cross section, not just the correction. 

 * They do not include the Coulomb term $\to$ Wrong value for $a_\tau$ obtained. 


\subsubsection{$\tau$-pair production with leptonic $\tau$-decays}

- Comparison including leptonic $\tau$-decays.

- Show the comparison between $\sigma^\mr{QED}_\mr{P}$ vs $\sigma^{\mr{FF}}$.

- Show the comparison between $\sigma^\mr{NLO}$ vs $\sigma^{\mr{FF}} + \Delta\sigma^\NLO_\mr{D} + \Delta\sigma^\NLO_{\overline{\mr{D}}}$.

- Remark the importance of including the corrections to the decays in the form-factor calculation (or of extracting these corrections to the fixed-order calculation).
Specially if $p_{\mr{T},\mu}$ is employed in the analysis.  

\subsubsection*{Fixed photon--photon centre-of-mass energy (?)}

- Show inclusive predictions for fixed c.m.e.

- Remark again the dominance of the Coulomb term in the NLO correction for small c.m.e. 

- Show that the sensitivity of $p_{\mr{T},\mu}$ to collinear radiation off the produced $\tau$-leptons is not determinant and, thus, it is a good observable.


\subsubsection*{ATLAS set-up}

- Show the comparison for the ATLAS set-up.

- Comment that the Coulomb contribution is suppressed (neglectable) here due to the presence of $p_{\mr{T},\ell}$ cuts.

\subsubsection*{Dependence on the choice of $p_{\mr{T},\ell}$ cuts}

- Show the comparison for $p_{\mr{T},\ell} > 2, 4, 6 \GeV$.

- Comment the problem of having a large $p_{\mr{T},\ell}$ cut if enough precision is reached.


\subsubsection*{Spin-correlation effects (?)}

\subsection{Impact of BSM contributions to $a_\tau$ in the cross section}

- Show plot with different values of $a_\tau$. (Maybe use $a_\tau^\mr{SM} + a_\tau^\mr{BSM}$).

\subsection{Impact of BSM contributions to $d_\tau$ in the cross section}

- $d_\tau^\mr{SM} = 0$.

- $\order{d_\tau^\mr{BSM}} \to 0$.

- $\order{(d_\tau^\mr{BSM})^2}$ terms needed.

\section{Conclusion}
\label{sec:conclusion}



\appendix
\section*{Appendix}



\newpage

\bibliographystyle{utphys.bst}
\bibliography{aa-tautau}


\end{document}



